---
title: Can you combine two aregImpute objects?
author: Harris
date: '2017-08-08'
slug: can-you-combine-two-aregimpute-objects
categories:
  - R
tags:
  - question
---

In order to parallelize `Hmisc::aregImpute()`, we need to know if we can divide the imputations across multiple cores and combine the output objects.

## Setup

Example impute code is from https://www.rdocumentation.org/packages/Hmisc/versions/4.0-3/topics/aregImpute.
```{r}
library("Hmisc")
library("tidyverse")
library("broom")
```

## Run `n.impute = 50`

```{r}
set.seed(3)
x1 <- rnorm(200)
x2 <- x1^2
x3 <- runif(200)
m <- 30
x2[1:m] <- NA
a <- aregImpute(~x1+x2+I(x3), n.impute=50, nk=4, match='closest') # output clipped for SO
a
matplot(x1[1:m]^2, a$imputed$x2)
abline(a=0, b=1, lty=2)

# x1[1:m]^2
# a$imputed$x2
```
### Structure of `a`

```{r}
str(a)
```

## Proposed combine function

From my naive interpretation, it seems like the worst sin might be `rsq=areg2$rsq`.


```{r}
c_aregImpute <- function(areg1, areg2){
  call <- areg1$call
  call[["n.impute"]] <- areg1$n.impute + areg2$n.impute
  structure(list(call=call,
                 formula=areg1$formula,
                 match=areg1$match,
                 fweighted=areg1$fweighted,
                 pmmtype=areg1$pmmtype,
                 n=areg1$n,
                 p=areg1$p,
                 na=areg1$na,
                 nna=areg1$nna,
                 type=areg1$type,
                 tlinear=areg1$tlinear,
                 nk=areg1$nk,
                 cat.levels=areg1$cat.levels,
                 df=areg1$df,
                 n.impute=areg1$n.impute + areg2$n.impute,
                 imputed=mapply(cbind,areg1$imputed, areg2$imputed),
                 x=areg1$x,
                 rsq=areg2$rsq,
                 resampacc=areg1$resampacc),
            class='aregImpute')
}
```

## Run two `n.impute = 25`

```{r}
a1 <- aregImpute(~x1+x2+I(x3), n.impute=25, nk=4, match='closest') # output clipped for SO
a2 <- aregImpute(~x1+x2+I(x3), n.impute=25, nk=4, match='closest') # output clipped for SO

ca <- c_aregImpute(a1, a2)
```

## comparing `rsq` from examples.

```{r}
list(a=a$rsq , a1= a1$rsq, a2 = a2$rsq, ca = ca$rsq)
```

## comparing `a` and `ca` from examples.

```{r}
a
ca
```

## Comparing `matplot`

```{r}
matplot(x1[1:m]^2, ca$imputed$x2)
matplot(x1[1:m]^2, a$imputed$x2)
